Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-02 src/article.tex
Add version number
Revise title and contact details
Proof read abstract

\title{Scaffolder - Software for Microbial Genome Scaffolding.} %{{{1

\author{
  Michael D Barton$^{1}$\correspondingauthor%
  \email{Michael D Barton\correspondingauthor  - mail@nucleotid.es}%
\and
  Hazel A Barton$^1$%
  \email{Hazel A Barton - bartonh@nku.edu}%
      }

@@

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of sequences. Therefore a common step in a genome project
  is to join neighbouring sequence regions together and fill gaps in the
  assembly using additional sequence. This scaffolding step, however, is
  non-trivial and requires manually editing large blocks of nucleotide
  sequence. Joining sequence contigs together also hides the source of each
  region in the final genome sequence. Taken together, these considerations may
  make reproducing or editing an existing genome build difficult.

  \paragraph*{Methods:} The software outlined here, ``Scaffolder'', is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using YAML
  - a markup language, which is both human and machine-readable. Command line
  binaries and extensive documentation are available.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple format to write
  and edit scaffold file syntax. This syntax further allows  unknown regions to
  be defined, and inserts to be added to the scaffold to fill gaps. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit and compare than FASTA sequence.

@@

  \begin{description}
    \item[Project name:] Scaffolder
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Debian.
    \item[Programming language:] Ruby
    \item[Other requirements:] RubyGems
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}

>>>>

\title{Scaffolder - Software for Reproducible Genome Scaffolding.} %{{{1

\author{
  Michael D Barton$^{1}$\correspondingauthor%
  \email{Michael D Barton\correspondingauthor  - mail@michaelbarton.me.uk}%
\and
  Hazel A Barton$^1$%
  \email{Hazel A Barton - bartonh@nku.edu}%
      }

@@

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps in the assembly using additional sequence. This scaffolding
  step, however, is non-trivial and requires manually editing large blocks of
  nucleotide sequence. Joining sequence contigs together also hides the source
  of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined here, ``Scaffolder'', is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using YAML
  - a data format, which is both human and machine-readable. Command line
  binaries and extensive documentation are available.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent sequences using a relatively simple format to write
  and edit scaffold file syntax. This syntax further allows  unknown regions to
  be defined, and inserts to be added to the scaffold to fill gaps. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit and compare than FASTA nucleotide sequence.

@@

  \begin{description}
    \item[Project name:] Scaffolder, version 0.4.1
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Debian.
    \item[Programming language:] Ruby
    \item[Other requirements:] RubyGems
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}
